---
title: "Homework assignment no. 1"
author: "Piotr Cieslak"
date: '2022-11-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("cieslak_piotr_assignment_1.R")
```

```{r packages, cache=TRUE}
library(sqldf)
library(dplyr)
library(data.table)
library(microbenchmark)
```

```{r data, cache=TRUE, dependson="packages"}

Posts <- read.csv("/home/piotrcieslak/mini/data_processing/hw1/travel_stackexchange_com/Posts.csv.gz")
Users <- read.csv("/home/piotrcieslak/mini/data_processing/hw1/travel_stackexchange_com/Users.csv.gz")
Badges <- read.csv("/home/piotrcieslak/mini/data_processing/hw1/travel_stackexchange_com/Badges.csv.gz")
Comments <- read.csv("/home/piotrcieslak/mini/data_processing/hw1/travel_stackexchange_com/Comments.csv.gz")
Votes <- read.csv("/home/piotrcieslak/mini/data_processing/hw1/travel_stackexchange_com/Votes.csv.gz")

```

## Introduction

This report contains comments, benchmarks and test of correctness of the solutions to assignment number 1
from Data Processing in R and Python. Below I explain each query from the assignment.

## Queries

Each subsection is dedicated for one query. In every one of them I placed the interpretation of the query,
tests, whether each of my solutions is equivalent to the expected result, and benchmarks. Note: I used dplyr::all_equals() function to test the equivalency.

* ### Query 1


  
  ##### Interpretation

  The first query returns number of all posts made in each year.

  ##### Test of equivalency
  
  ```{r}
  dplyr::all_equal(sqldf_1(Posts), base_1(Posts))
  dplyr::all_equal(sqldf_1(Posts), dplyr_1(Posts))
  dplyr::all_equal(sqldf_1(Posts), data.table_1(Posts))
  ```
  
  ##### Benchmark
  
  ```{r echo=FALSE}
  microbenchmark::microbenchmark(
    sqldf=sqldf_1(Posts),
    base=base_1(Posts),
    dplyr=dplyr_1(Posts),
    data.table=data.table_1(Posts)
  )
  ```
  
* ### Query 2
  
  
  
  #### Interpretation
  
  The second query returns the id and name of top 10 users who are authors
  of posts of type question with the most number of views on
  those posts.
  
  ##### Test of equivalency
  
  ```{r}
  dplyr::all_equal(sqldf_2(Users, Posts), base_2(Users, Posts))
  dplyr::all_equal(sqldf_2(Users, Posts), dplyr_2(Users, Posts))
  dplyr::all_equal(sqldf_2(Users, Posts), data.table_2(Users, Posts))
  ```
  
  ##### Benchmark
  
  ```{r echo=FALSE}
  microbenchmark::microbenchmark(
    sqldf=sqldf_2(Users, Posts),
    base=base_2(Users, Posts),
    dplyr=dplyr_2(Users, Posts),
    data.table=data.table_2(Users, Posts)
  )
  ```
 
* ### Query 3
  
  
  
  ##### Interpretation

  The third query returns the most frequently given Badge every year.
  
  ##### Test of equivalency
  
  ```{r}
  dplyr::all_equal(sqldf_3(Badges), base_3(Badges))
  dplyr::all_equal(sqldf_3(Badges), dplyr_3(Badges))
  dplyr::all_equal(sqldf_3(Badges), data.table_3(Badges))
  ```
  
  ##### Benchmark
  
  ```{r echo=FALSE}
  microbenchmark::microbenchmark(
    sqldf=sqldf_3(Badges),
    base=base_3(Badges),
    dplyr=dplyr_3(Badges),
    data.table=data.table_3(Badges)
  )
  ```
  
* ### Query 4
  
  
  
  ##### Interpretation

  The fourth query returns top 10 posts with the biggest cumulated comments
  score, along with title of each post, number of all comments, post view count, 
  name of the author and author's reputation.
  
  ##### Test of equivalency
  
  
  ```{r}
  dplyr::all_equal(sqldf_4(Comments, Posts, Users), base_4(Comments, Posts, Users))
  dplyr::all_equal(sqldf_4(Comments, Posts, Users), dplyr_4(Comments, Posts, Users))
  dplyr::all_equal(sqldf_4(Comments, Posts, Users), data.table_4(Comments, Posts, Users))
  ```
  
  ##### Benchmark
  
  ```{r echo=FALSE}
  microbenchmark::microbenchmark(
    sqldf=sqldf_4(Comments, Posts, Users),
    base=base_4(Comments, Posts, Users),
    dplyr=dplyr_4(Comments, Posts, Users),
    data.table=data.table_4(Comments, Posts, Users)
  )
  ```
  
* ### Query 5
  
  
  
  ##### Interpretation

  The fifth query returns top 20 posts with the biggest number of votes made during
  covid pandemic (between the year 2019 and 2021 and votes are either spam, 
  offensive votes or downvotes), along with date of creation of each post, post id
  and sum of votes made during any period.
  
  ##### Test of equivalency
  
  ```{r}
  dplyr::all_equal(sqldf_5(Posts, Votes), base_5(Posts, Votes), convert = TRUE)
  dplyr::all_equal(sqldf_5(Posts, Votes), dplyr_5(Posts, Votes), convert = TRUE)
  dplyr::all_equal(sqldf_5(Posts, Votes), data.table_5(Posts, Votes), convert = TRUE)
  ```
  
  ##### Benchmark
  
  ```{r echo=FALSE}
  microbenchmark::microbenchmark(
    sqldf=sqldf_5(Posts, Votes),
    base=base_5(Posts, Votes),
    dplyr=dplyr_5(Posts, Votes),
    data.table=data.table_5(Posts, Votes)
  )
  ```
  
  ### Conclusions
  
  From the results of the microbenchmark function, we can see that the fastest are solutions
  that use data.table library for data wrangling. One of the reasons is the implementation of
  *order* function, which is fast and very carefully implemented. Data.table developing team also
  remains active, in contrast to developers of other libraries, and are constantly optimizing their
  internal algorythms, which cause data.table functions to scale better and better.

  
